Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
        \label{fig:original}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
        \caption{Controller synthesised by \tool.}
        \label{fig:cegiscontroller}
    \end{subfigure}
    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
\end{figure}

Figure~\ref{fig:step} shows the step responses of the closed-loop system 
with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), 
the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}). 
The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize 
the closed-loop system without uncertainties, but it is rejected by \tool since this solution 
is not considered to be sound. Finally, Figure~\ref{fig:step2} shows a stable behavior 
for the final (sound) solution, which presents a lower settling time.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
        \caption{Orignal controller.}
        \label{fig:step0}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
        \caption{First candidate solution.}
        \label{fig:step1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
        \caption{Final solution by \tool.}
        \label{fig:step2}
    \end{subfigure}
    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesise} step of \tool.}\label{fig:step}
\end{figure*}
